Human Deamination Read Length Analysis

### 2022-05-11 R/HumanDeaminationReadLengthAnalysis.rmd
Update HumanDeaminationReadLengthAnalysis.rmd
Removed previous "non-lesion-anchored" analysis.

```{r get_file_paths_1}
# Get file paths for the mismatch by read data
CPDMismatchDataFilePaths = list(rep1 = list(), rep2 = list())
CPDMismatchDataFilePaths$rep1 = list(
  hr1 = file.path(deaminationDataDirectory, "mismatches_by_read", "NHF1_CPD_1h_Rep1_mismatches_by_read.bed"),
  hr8 = file.path(deaminationDataDirectory, "mismatches_by_read", "NHF1_CPD_8h_Rep1_mismatches_by_read.bed"),
  hr24 = file.path(deaminationDataDirectory, "mismatches_by_read", "NHF1_CPD_24h_Rep1_mismatches_by_read.bed"),
  hr48 = file.path(deaminationDataDirectory, "mismatches_by_read", "NHF1_CPD_48h_Rep1_mismatches_by_read.bed")
)
CPDMismatchDataFilePaths$rep2 = list(
  hr1 = file.path(deaminationDataDirectory, "mismatches_by_read", "NHF1_CPD_1h_Rep2_mismatches_by_read.bed"),
  hr8 = file.path(deaminationDataDirectory, "mismatches_by_read", "NHF1_CPD_8h_Rep2_mismatches_by_read.bed"),
  hr24 = file.path(deaminationDataDirectory, "mismatches_by_read", "NHF1_CPD_24h_Rep2_mismatches_by_read.bed"),
  hr48 = file.path(deaminationDataDirectory, "mismatches_by_read", "NHF1_CPD_48h_Rep2_mismatches_by_read.bed")
)

sixFourMismatchDataFilePaths = list(rep1 = list(), rep2 = list())
sixFourMismatchDataFilePaths$rep1 = list(
  min5 = file.path(deaminationDataDirectory, "mismatches_by_read", "NHF1_6-4-PP_5min_Rep1_mismatches_by_read.bed"),
  min20 = file.path(deaminationDataDirectory, "mismatches_by_read", "NHF1_6-4-PP_20min_Rep1_mismatches_by_read.bed"),
  hr1 = file.path(deaminationDataDirectory, "mismatches_by_read", "NHF1_6-4-PP_1h_Rep1_mismatches_by_read.bed")
)
sixFourMismatchDataFilePaths$rep2 = list(
  min5 = file.path(deaminationDataDirectory, "mismatches_by_read", "NHF1_6-4-PP_5min_Rep2_mismatches_by_read.bed"),
  min20 = file.path(deaminationDataDirectory, "mismatches_by_read", "NHF1_6-4-PP_20min_Rep2_mismatches_by_read.bed"),
  hr1 = file.path(deaminationDataDirectory, "mismatches_by_read", "NHF1_6-4-PP_1h_Rep2_mismatches_by_read.bed")
)
```

```{r acquire_and_format_data_1}
CPDMismatchData = lapply(CPDMismatchDataFilePaths, function(x) lapply(x, fread))
sixFourMismatchData = lapply(sixFourMismatchDataFilePaths, function(x) lapply(x, fread))

# Create a subset of single mismatch C>T reads.
CPDSingleCToTMismatchData = lapply(CPDMismatchData, function(x) lapply(
  x, function(y) filterResults(y[V5 == "C>T"], minReadLength = 23, maxReadLength = 31)
))
sixFourSingleCToTMismatchData = lapply(sixFourMismatchData, function(x) lapply(
  x, function(y) filterResults(y[V5 == "C>T"], minReadLength = 23, maxReadLength = 31)
))

# Simplify the data
CPDSingleCToTMismatchData = lapply(CPDSingleCToTMismatchData, function(x) lapply(
  x, function(y) simplifyTable(y, TRUE)
))
sixFourSingleCToTMismatchData = lapply(sixFourSingleCToTMismatchData, function(x) lapply(
  x, function(y) simplifyTable(y, TRUE)
))

```

```{r filter_by_mismatch_pos_and_read_length_1}
CPDPeakCToTMismatchData = lapply(CPDSingleCToTMismatchData, function(x) {
  lapply(x, filterMismatchesByPositionAndReadLength, HUMAN_THREE_PRIME_POS_CONSTRAINTS)
})
CPDFirstQPeakCToTMismatchData = lapply(CPDPeakCToTMismatchData, function(x) {
  lapply(x, getFirstPositionQuartile)
})
CPDLastQPeakCToTMismatchData = lapply(CPDPeakCToTMismatchData, function(x) {
  lapply(x, getLastPositionQuartile)
})

sixFourPeakCToTMismatchData = lapply(sixFourSingleCToTMismatchData, function(x) {
  lapply(x, filterMismatchesByPositionAndReadLength, HUMAN_THREE_PRIME_POS_CONSTRAINTS)
})
sixFourFirstQPeakCToTMismatchData = lapply(sixFourPeakCToTMismatchData, function(x) {
  lapply(x, getFirstPositionQuartile)
})
sixFourLastQPeakCToTMismatchData = lapply(sixFourPeakCToTMismatchData, function(x) {
  lapply(x, getLastPositionQuartile)
})
```

```{r generate_nucleotide_frequency_data_1}
CPDSingleCToTNucFreq = lapply(CPDSingleCToTMismatchData, tabulateNucFreqByPosTimepointAndLength)
CPDFirstQPeakCToTNucFreq = lapply(CPDFirstQPeakCToTMismatchData, tabulateNucFreqByPosTimepointAndLength)
CPDLastQPeakCToTNucFreq = lapply(CPDLastQPeakCToTMismatchData, tabulateNucFreqByPosTimepointAndLength)

sixFourSingleCToTNucFreq = lapply(sixFourSingleCToTMismatchData, tabulateNucFreqByPosTimepointAndLength)
sixFourFirstQPeakCToTNucFreq = lapply(sixFourFirstQPeakCToTMismatchData, tabulateNucFreqByPosTimepointAndLength)
sixFourLastQPeakCToTNucFreq = lapply(sixFourLastQPeakCToTMismatchData, tabulateNucFreqByPosTimepointAndLength)
```

```{r purine_vs_pyrimidine_frequencies_across_read_length, fig.width = 11, fig.height = 5}
plotNucFreqVsReadLengthBarPlot(CPDSingleCToTNucFreq$rep1, title = "CPD Rep1 3' Nuc Freq",
                               combineNucleotides = c("AG","CT"), combinedNames = c("Purine","Pyrimidine"))
plotNucFreqVsReadLengthBarPlot(CPDSingleCToTNucFreq$rep2, title = "CPD Rep2 3' Nuc Freq",
                               combineNucleotides = c("AG","CT"), combinedNames = c("Purine","Pyrimidine"))

plotNucFreqVsReadLengthBarPlot(sixFourSingleCToTNucFreq$rep1, title = "6-4 Rep1 3' Nuc Freq",
                               combineNucleotides = c("AG","CT"), combinedNames = c("Purine","Pyrimidine"))
plotNucFreqVsReadLengthBarPlot(sixFourSingleCToTNucFreq$rep2, title = "6-4 Rep2 3' Nuc Freq",
                               combineNucleotides = c("AG","CT"), combinedNames = c("Purine","Pyrimidine"))
```

```{r purine_vs_pyrimidine_frequencies_first_quartile_mismatch_pos, fig.width = 11, fig.height = 5}
plotNucFreqVsReadLengthBarPlot(CPDFirstQPeakCToTNucFreq$rep1, title = "CPD Rep1 1st Quartile Nuc Freq",
                               combineNucleotides = c("AG","CT"), combinedNames = c("Purine","Pyrimidine"))
plotNucFreqVsReadLengthBarPlot(CPDFirstQPeakCToTNucFreq$rep2, title = "CPD Rep2 1st Quartile Nuc Freq",
                               combineNucleotides = c("AG","CT"), combinedNames = c("Purine","Pyrimidine"))

plotNucFreqVsReadLengthBarPlot(sixFourFirstQPeakCToTNucFreq$rep1, title = "6-4 Rep1 1st Quartile Nuc Freq",
                               combineNucleotides = c("AG","CT"), combinedNames = c("Purine","Pyrimidine"))
plotNucFreqVsReadLengthBarPlot(sixFourFirstQPeakCToTNucFreq$rep2, title = "6-4 Rep2 1st Quartile Nuc Freq",
                               combineNucleotides = c("AG","CT"), combinedNames = c("Purine","Pyrimidine"))
```

```{r purine_vs_pyrimidine_frequencies_last_quartile_mismatch_pos, fig.width = 11, fig.height = 5}
plotNucFreqVsReadLengthBarPlot(CPDLastQPeakCToTNucFreq$rep1, title = "CPD Rep1 4th Quartile Nuc Freq",
                               combineNucleotides = c("AG","CT"), combinedNames = c("Purine","Pyrimidine"))
plotNucFreqVsReadLengthBarPlot(CPDLastQPeakCToTNucFreq$rep2, title = "CPD Rep2 4th Quartile Nuc Freq",
                               combineNucleotides = c("AG","CT"), combinedNames = c("Purine","Pyrimidine"))

plotNucFreqVsReadLengthBarPlot(sixFourLastQPeakCToTNucFreq$rep1, title = "6-4 Rep1 4th Quartile Nuc Freq",
                               combineNucleotides = c("AG","CT"), combinedNames = c("Purine","Pyrimidine"))
plotNucFreqVsReadLengthBarPlot(sixFourLastQPeakCToTNucFreq$rep2, title = "6-4 Rep2 4th Quartile Nuc Freq",
                               combineNucleotides = c("AG","CT"), combinedNames = c("Purine","Pyrimidine"))
```

```{r get_file_paths_2}
# Get file paths for the expanded mismatch by read data
expandedCPDMismatchDataFilePaths = list(rep1 = list(), rep2 = list())
expandedCPDMismatchDataFilePaths$rep1 = list(
  hr1 = file.path(deaminationDataDirectory, "mismatches_by_read",
                  "NHF1_CPD_1h_Rep1_mismatches_by_read_3bp_expanded.bed"),
  hr8 = file.path(deaminationDataDirectory, "mismatches_by_read",
                  "NHF1_CPD_8h_Rep1_mismatches_by_read_3bp_expanded.bed"),
  hr24 = file.path(deaminationDataDirectory, "mismatches_by_read",
                   "NHF1_CPD_24h_Rep1_mismatches_by_read_3bp_expanded.bed"),
  hr48 = file.path(deaminationDataDirectory, "mismatches_by_read",
                   "NHF1_CPD_48h_Rep1_mismatches_by_read_3bp_expanded.bed")
)
expandedCPDMismatchDataFilePaths$rep2 = list(
  hr1 = file.path(deaminationDataDirectory, "mismatches_by_read",
                  "NHF1_CPD_1h_Rep2_mismatches_by_read_3bp_expanded.bed"),
  hr8 = file.path(deaminationDataDirectory, "mismatches_by_read",
                  "NHF1_CPD_8h_Rep2_mismatches_by_read_3bp_expanded.bed"),
  hr24 = file.path(deaminationDataDirectory, "mismatches_by_read",
                   "NHF1_CPD_24h_Rep2_mismatches_by_read_3bp_expanded.bed"),
  hr48 = file.path(deaminationDataDirectory, "mismatches_by_read",
                   "NHF1_CPD_48h_Rep2_mismatches_by_read_3bp_expanded.bed")
)

expandedSixFourMismatchDataFilePaths = list(rep1 = list(), rep2 = list())
expandedSixFourMismatchDataFilePaths$rep1 = list(
  min5 = file.path(deaminationDataDirectory, "mismatches_by_read",
                   "NHF1_6-4-PP_5min_Rep1_mismatches_by_read_3bp_expanded.bed"),
  min20 = file.path(deaminationDataDirectory, "mismatches_by_read",
                    "NHF1_6-4-PP_20min_Rep1_mismatches_by_read_3bp_expanded.bed"),
  hr1 = file.path(deaminationDataDirectory, "mismatches_by_read",
                  "NHF1_6-4-PP_1h_Rep1_mismatches_by_read_3bp_expanded.bed")
)
expandedSixFourMismatchDataFilePaths$rep2 = list(
  min5 = file.path(deaminationDataDirectory, "mismatches_by_read",
                   "NHF1_6-4-PP_5min_Rep2_mismatches_by_read_3bp_expanded.bed"),
  min20 = file.path(deaminationDataDirectory, "mismatches_by_read",
                    "NHF1_6-4-PP_20min_Rep2_mismatches_by_read_3bp_expanded.bed"),
  hr1 = file.path(deaminationDataDirectory, "mismatches_by_read",
                  "NHF1_6-4-PP_1h_Rep2_mismatches_by_read_3bp_expanded.bed")
)
```

```{r acquire_and_format_data_2}
expandedCPDSingleCToTMismatchData = lapply(expandedCPDMismatchDataFilePaths, function(x) lapply(x, fread))
expandedSixFourSingleCToTMismatchData = lapply(expandedSixFourMismatchDataFilePaths, function(x) lapply(x, fread))
expansionOffset = 3

@@

```{r generate_nucleotide_frequency_data_2}
threePrimeMismatchCPDNucFreq = lapply(threePrimeMismatchAnchoredCPDData, tabulateNucFreqByPosTimepointAndLength)
fivePrimeMismatchCPDNucFreq = lapply(fivePrimeMismatchAnchoredCPDData,
                                     tabulateNucFreqByPosTimepointAndLength, posType = FIVE_PRIME)

@@

>>>>

```{r get_file_paths}
expansionOffset = 10

# Get file paths for the expanded mismatch by read data
expandedCPDMismatchDataFilePaths = list(rep1 = list(), rep2 = list())
expandedCPDMismatchDataFilePaths$rep1 = list(
  hr1 = file.path(deaminationDataDirectory, "mismatches_by_read",
                  paste0("NHF1_CPD_1h_Rep1_mismatches_by_read_",expansionOffset,"bp_expanded.bed")),
  hr8 = file.path(deaminationDataDirectory, "mismatches_by_read",
                  paste0("NHF1_CPD_8h_Rep1_mismatches_by_read_",expansionOffset,"bp_expanded.bed")),
  hr24 = file.path(deaminationDataDirectory, "mismatches_by_read",
                   paste0("NHF1_CPD_24h_Rep1_mismatches_by_read_",expansionOffset,"bp_expanded.bed")),
  hr48 = file.path(deaminationDataDirectory, "mismatches_by_read",
                   paste0("NHF1_CPD_48h_Rep1_mismatches_by_read_",expansionOffset,"bp_expanded.bed"))
)
expandedCPDMismatchDataFilePaths$rep2 = list(
  hr1 = file.path(deaminationDataDirectory, "mismatches_by_read",
                  paste0("NHF1_CPD_1h_Rep2_mismatches_by_read_",expansionOffset,"bp_expanded.bed")),
  hr8 = file.path(deaminationDataDirectory, "mismatches_by_read",
                  paste0("NHF1_CPD_8h_Rep2_mismatches_by_read_",expansionOffset,"bp_expanded.bed")),
  hr24 = file.path(deaminationDataDirectory, "mismatches_by_read",
                   paste0("NHF1_CPD_24h_Rep2_mismatches_by_read_",expansionOffset,"bp_expanded.bed")),
  hr48 = file.path(deaminationDataDirectory, "mismatches_by_read",
                   paste0("NHF1_CPD_48h_Rep2_mismatches_by_read_",expansionOffset,"bp_expanded.bed"))
)

expandedSixFourMismatchDataFilePaths = list(rep1 = list(), rep2 = list())
expandedSixFourMismatchDataFilePaths$rep1 = list(
  min5 = file.path(deaminationDataDirectory, "mismatches_by_read",
                   paste0("NHF1_6-4-PP_5min_Rep1_mismatches_by_read_",expansionOffset,"bp_expanded.bed")),
  min20 = file.path(deaminationDataDirectory, "mismatches_by_read",
                    paste0("NHF1_6-4-PP_20min_Rep1_mismatches_by_read_",expansionOffset,"bp_expanded.bed")),
  hr1 = file.path(deaminationDataDirectory, "mismatches_by_read",
                  paste0("NHF1_6-4-PP_1h_Rep1_mismatches_by_read_",expansionOffset,"bp_expanded.bed"))
)
expandedSixFourMismatchDataFilePaths$rep2 = list(
  min5 = file.path(deaminationDataDirectory, "mismatches_by_read",
                   paste0("NHF1_6-4-PP_5min_Rep2_mismatches_by_read_",expansionOffset,"bp_expanded.bed")),
  min20 = file.path(deaminationDataDirectory, "mismatches_by_read",
                    paste0("NHF1_6-4-PP_20min_Rep2_mismatches_by_read_",expansionOffset,"bp_expanded.bed")),
  hr1 = file.path(deaminationDataDirectory, "mismatches_by_read",
                  paste0("NHF1_6-4-PP_1h_Rep2_mismatches_by_read_",expansionOffset,"bp_expanded.bed"))
)
```

```{r acquire_and_format_data}
expandedCPDSingleCToTMismatchData = lapply(expandedCPDMismatchDataFilePaths, function(x) lapply(x, fread))
expandedSixFourSingleCToTMismatchData = lapply(expandedSixFourMismatchDataFilePaths, function(x) lapply(x, fread))

@@

```{r generate_nucleotide_frequency_data}
threePrimeMismatchCPDNucFreq = lapply(threePrimeMismatchAnchoredCPDData, tabulateNucFreqByPosTimepointAndLength)
fivePrimeMismatchCPDNucFreq = lapply(fivePrimeMismatchAnchoredCPDData,
                                     tabulateNucFreqByPosTimepointAndLength, posType = FIVE_PRIME)

@@

```{r CPD_mismatch__anchored_nucleotide_frequencies, fig.width = 11, fig.height = 7}
plotNucFreqVsReadLengthBarPlot(threePrimeMismatchSixFourNucFreq$rep1, 
                               title = "6-4 3' Anchored Nucleotide Frequencies Rep1",
                               secondaryYAxisLabel = "5' Cut Site Distance",
                               posType = THREE_PRIME, showFivePrimeCutSite = TRUE, expansionOffset = expansionOffset)
plotNucFreqVsReadLengthBarPlot(threePrimeMismatchSixFourNucFreq$rep2, 
                               title = "6-4 3' Anchored Nucleotide Frequencies Rep2",
                               secondaryYAxisLabel = "5' Cut Site Distance",
                               posType = THREE_PRIME, showFivePrimeCutSite = TRUE, expansionOffset = expansionOffset)

plotNucFreqVsReadLengthBarPlot(fivePrimeMismatchSixFourNucFreq$rep1, 
                               title = "6-4 5' Anchored Nucleotide Frequencies Rep1",
                               yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "3' Cut Site Distance",
                               posType = FIVE_PRIME, showThreePrimeCutSite = TRUE, expansionOffset = expansionOffset)
plotNucFreqVsReadLengthBarPlot(fivePrimeMismatchSixFourNucFreq$rep2, 
                               title = "6-4 5' Anchored Nucleotide Frequencies Rep2",
                               yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "3' Cut Site Distance",
                               posType = FIVE_PRIME, showThreePrimeCutSite = TRUE, expansionOffset = expansionOffset)
```

```{r CPD_mismatch_anchored_purine_frequencies, fig.width = 11, fig.height = 7}
plotNucFreqVsReadLengthBarPlot(threePrimeMismatchSixFourNucFreq$rep1, 
                               title = "6-4 3' Anchored Purine Frequencies Rep1",
                               yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "5' Cut Site Distance",
                               combineNucleotides = c("AG"), combinedNames = c("Purine"),
                               posType = THREE_PRIME, showFivePrimeCutSite = TRUE, expansionOffset = expansionOffset)
plotNucFreqVsReadLengthBarPlot(threePrimeMismatchSixFourNucFreq$rep2, 
                               title = "6-4 3' Anchored Purine Frequencies Rep2",
                               yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "5' Cut Site Distance",
                               combineNucleotides = c("AG"), combinedNames = c("Purine"),
                               posType = THREE_PRIME, showFivePrimeCutSite = TRUE, expansionOffset = expansionOffset)

plotNucFreqVsReadLengthBarPlot(fivePrimeMismatchSixFourNucFreq$rep1, 
                               title = "6-4 5' Anchored Purine Frequencies Rep1",
                               yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "3' Cut Site Distance",
                               combineNucleotides = c("AG"), combinedNames = c("Purine"),
                               posType = FIVE_PRIME, showThreePrimeCutSite = TRUE, expansionOffset = expansionOffset)
plotNucFreqVsReadLengthBarPlot(fivePrimeMismatchSixFourNucFreq$rep2, 
                               title = "6-4 5' Anchored Purine Frequencies Rep2",
                               yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "3' Cut Site Distance",
                               combineNucleotides = c("AG"), combinedNames = c("Purine"),
                               posType = FIVE_PRIME, showThreePrimeCutSite = TRUE, expansionOffset = expansionOffset)
```

```{r compute_sequence_enrichment}
threePrimeMMAnchoredCPDEnrichment = mapply(function(mismatchDataRep, nucFreqRep) {
  setNames(lapply(seq_along(mismatchDataRep), function(i) {
    getSequenceEnrichmentByReadLengthAndPos(mismatchDataRep[[i]],
                                            nucFreqRep[Timepoint == names(mismatchDataRep)[i]],
                                            c("CG","CA","TG","TA"))
  }), names(mismatchDataRep))
}, threePrimeMismatchAnchoredCPDData, threePrimeMismatchCPDNucFreq, SIMPLIFY = FALSE)

fivePrimeMMAnchoredCPDEnrichment = mapply(function(mismatchDataRep, nucFreqRep) {
  setNames(lapply(seq_along(mismatchDataRep), function(i) {
    getSequenceEnrichmentByReadLengthAndPos(mismatchDataRep[[i]],
                                            nucFreqRep[Timepoint == names(mismatchDataRep)[i]],
                                            c("TGG"), posType = FIVE_PRIME)
  }), names(mismatchDataRep))
}, fivePrimeMismatchAnchoredCPDData, fivePrimeMismatchCPDNucFreq, SIMPLIFY = FALSE)

threePrimeMMAnchoredSixFourEnrichment = mapply(function(mismatchDataRep, nucFreqRep) {
  setNames(lapply(seq_along(mismatchDataRep), function(i) {
    getSequenceEnrichmentByReadLengthAndPos(mismatchDataRep[[i]],
                                            nucFreqRep[Timepoint == names(mismatchDataRep)[i]],
                                            c("CG","CA","TG","TA"))
  }), names(mismatchDataRep))
}, threePrimeMismatchAnchoredSixFourData, threePrimeMismatchSixFourNucFreq, SIMPLIFY = FALSE)

fivePrimeMMAnchoredSixFourEnrichment = mapply(function(mismatchDataRep, nucFreqRep) {
  setNames(lapply(seq_along(mismatchDataRep), function(i) {
    getSequenceEnrichmentByReadLengthAndPos(mismatchDataRep[[i]],
                                            nucFreqRep[Timepoint == names(mismatchDataRep)[i]],
                                            c("TGG"), posType = FIVE_PRIME)
  }), names(mismatchDataRep))
}, fivePrimeMismatchAnchoredSixFourData, fivePrimeMismatchSixFourNucFreq, SIMPLIFY = FALSE)
```

```{r plot_CPD_sequence_enrichment, fig.width = 11, fig.height = 7}
plotSequenceEnrichment(threePrimeMMAnchoredCPDEnrichment$rep1,
                       title = "CPD 3' Anchored YR Enrichment Rep1", secondaryYAxisLabel = "5' Cut Site Distance",
                       showFivePrimeCutSite = TRUE, expansionOffset = expansionOffset,
                       querySequences = c("CG","CA","TG","TA"))
plotSequenceEnrichment(threePrimeMMAnchoredCPDEnrichment$rep2,
                       title = "CPD 3' Anchored YR Enrichment Rep2", secondaryYAxisLabel = "5' Cut Site Distance",
                       showFivePrimeCutSite = TRUE, expansionOffset = expansionOffset,
                       querySequences = c("CG","CA","TG","TA"))

plotSequenceEnrichment(fivePrimeMMAnchoredCPDEnrichment$rep1,
                       title = "CPD 5' Anchored TGG Enrichment Rep1", secondaryYAxisLabel = "3' Cut Site Distance",
                       showThreePrimeCutSite = TRUE, expansionOffset = expansionOffset, posType = FIVE_PRIME,
                       querySequences = c("TGG"))
plotSequenceEnrichment(fivePrimeMMAnchoredCPDEnrichment$rep2,
                       title = "CPD 5' Anchored TGG Enrichment Rep2", secondaryYAxisLabel = "3' Cut Site Distance",
                       showThreePrimeCutSite = TRUE, expansionOffset = expansionOffset, posType = FIVE_PRIME,
                       querySequences = c("TGG"))
```

```{r enrichment_test_1}
for (i in 1:5) {
  testTable = data.table(Read_Length = 9,
                         Read_Sequence = replicate(1000, paste0(sample(c('A','C','G','T'), 9, TRUE), collapse = '')))
  testTableNucFreq = tabulateNucFreqByPosTimepointAndLength(testTable)
  testEnrichment = getSequenceEnrichmentByReadLengthAndPos(testTable, testTableNucFreq, c("CG","CA","TG","TA"))
  plotSequenceEnrichment(testEnrichment, title = "CPD 3' Anchored YR Enrichment Rep1")
}
```

```{r enrichment_test_2}
for (i in 1:5) {
  testTable = data.table(Read_Length = 9,
                         Read_Sequence = replicate(1000,
                                                   paste0(sample(c(rep('A',6),rep('C',4),rep('G',4),rep('T',6)),
                                                                 9, TRUE), collapse = '')))
  testTableNucFreq = tabulateNucFreqByPosTimepointAndLength(testTable)
  testEnrichment = getSequenceEnrichmentByReadLengthAndPos(testTable, testTableNucFreq, c("CG","CA","TG","TA"))
  plotSequenceEnrichment(testEnrichment, title = "CPD 3' Anchored YR Enrichment Rep1")
}
```
